Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-21 paper.qmd
Update Figure 3

sc_ltr_pos <- c(0.08, 0.96)
# sc_xlims <- c(-0.5, 1.47)
# sc_ylims <- c(-0.32, 2.1)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.3, 2)

@@

```{r}
## Compute hexbin parameters
num_bins_x_scurve <- 7

## hexagon binning to have regular hexagons
hb_obj_scurve <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = num_bins_x_scurve, 
  r2 = r2,
  q = 0.1)

@@

hex_grid_nonempty_scurve <-  ggplot(
  data = hex_grid_nonempty, 
  aes(x = x, y = y)) +
  geom_polygon(color = "black", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = df_bin_centroids, 
             aes(x = c_x, y = c_y), 
             color = "#33a02c") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("c", sc_ltr_pos) 
```

>>>>

sc_ltr_pos <- c(0.08, 0.95)
# sc_xlims <- c(-0.5, 1.47)
# sc_ylims <- c(-0.32, 2.1)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.2, 1)

@@

```{r}
## Compute hexbin parameters
num_bins_x_scurve <- 11

## hexagon binning to have regular hexagons
hb_obj_scurve <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = num_bins_x_scurve, 
  r2 = r2,
  q = 0.05)

@@

hex_grid_nonempty_scurve <-  ggplot(
  data = hex_grid_nonempty, 
  aes(x = x, y = y)) +
  geom_polygon(color = "black", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = df_bin_centroids, 
             aes(x = c_x, y = c_y), 
             color = "#33a02c",
             size = 0.5) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("c", sc_ltr_pos) 
```
